---
title: "Supplementary Materials for\nReaffirming the Role of the Hazard Ratio in Causal Inference"
fontsize: 12pt
geometry: margin=1in
output:
  bookdown::pdf_document2:
  keep_tex: yes
latex_engine: xelatex
md_extensions: +raw_attribute
number_sections: yes
# citation_package: natbib
longtable: yes
mainfont: Arial
header-includes:
- \DeclareUnicodeCharacter{2061}{}
- \usepackage{float} 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
tempFolder <- "e:/temp/simTemp"
```



# Extended simulations

In addition to the simulations described in the main manuscript, additional simulation scenarios were explored. 
The results are included in this section. 


The following additional variants were executed:

**True effect size**: for both the additive and multiplicative true effect sizes we included variants with 10 times large sizes. The *multiplicative (large) effect* uses the following function:

$$log⁡(HR(t))=10\mu_mWeibull(1.5,10)$$
the *additive (large) effect* uses:

$$RD(t)=10\mu_mWeibull(1,10)$$
**Incidence**: The background incidence in the original simulations are quite *high*:

$$h_(i,0)(t)=c_iWeibull(1,50)$$

Here we include a variant with *low* incidence:

$$h_(i,0)(t)=0.1c_iWeibull(1,50)$$
**Frailty heterogeneity**: The orignal simulations used a relatively *low* heterogeneity of frailty, differing at most by a factor of 4:

$$c_i\sim U(0.5,2)$$
Here we include a variant with *high* heterogeneity:

$$c_i \sim U(0.1,10)$$

# Simulation results (type 1 and 2 error)

## Low frailty heterogeneity

\begin{figure}[H]
\centering
\includegraphics[width=1\linewidth]{Type1And2Errorlow0.pdf}
\caption{Type 1 and 2 error under different simulation scenarios when using low frailty heterogenneity}
\end{figure}

## High frailty heterogeneity

\begin{figure}[H]
\centering
\includegraphics[width=1\linewidth]{Type1And2Errorhigh0.pdf}
\caption{Type 1 and 2 error under different simulation scenarios when using high frailty heterogenneity}
\end{figure}

# Kaplan-Meier plots for simulations

This section contains one Kaplan Meier plot per simulation settings. 
Each simulation scenarios was executed multiple times (to compute type 1 and 2 error), and the actual plot in each simulation run may differ from what is depicted here.


```{r kmPlots, echo=FALSE, results="asis", warning=FALSE, message=FALSE}
kmPlots <- readRDS(file.path(tempFolder, "kmPlots.rds"))
template <- "%label%\n\n![Kaplan Meier curves using simulation parameters: %parameters%](%fileName%)\n\n\\pagebreak"
for (i in 1:nrow(kmPlots)) {
  writeLines(gsub("%label%", kmPlots$label[i], gsub("%parameters%",  gsub("#", "", kmPlots$label[i]), gsub("%fileName%", kmPlots$fileName[i], template))))
}
```
